\documentclass[10pt,a4paper]{report}
\usepackage[margin=2cm]{geometry} %to modify page layout
\usepackage{titlesec} %to hide chapter titles
\usepackage{enumitem} %to have control over how formatting on enumerated lists

%because it's 2017 and clickable table of contents is needed
\usepackage{hyperref}
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}

\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}

% TODO change after changes approved in meeting
\date{Effective 2022-03-31}
\title{Computer Science Students' Club Constitution}

%To hide these full page chapter title page things which are just a waste of paper
\titleformat{\chapter}[display] {\normalfont\bfseries}{}{0pt}{\Large}


\begin{document}
	\maketitle
	\newpage
	\begin{small}
		\tableofcontents
	\end{small}
	\newpage

	\chapter{Admin and Membership}

	\section{Names and Objectives}
		\subsection{Name}
			The name of the club shall be the Computer Science Students' Club (CSSC)

		\subsection{Objectives}
		The main objectives of the club are
			\begin{enumerate}[label=\alph*]
				\item To promote and facilitate education of students within the School of Computer Science and Software Engineering by
				\begin{enumerate}[label=\roman*]
					\item Promoting academic co-operation at all levels within the School
					\item Examining matters of mutual interest
					\item Encouraging discussion of and action on educational matters
					\item Fostering Staff-Student interaction
					\item Co-operating with other organisations to achieve the above aims
				\end{enumerate}
				\item To promote and facilitate social interaction of students within the School of Computer Science and Software Engineering at the University of Western Australia.
				\item To encourage and promote co-operation between the Club and other affiliated societies representative of University Interest.
				\item To do all such things as would appear necessary and proper for the benefit or advancement of members to the Club.
				\item To remain affiliated to the Societies Council.
			\end{enumerate}

	\section{Membership}
		\subsection{Ordinary membership}
			Ordinary membership shall be confined to
			\begin{enumerate}[label=\alph*]
				\item Members of the Guild
				\item Associates of the Guild
				\item Honorary Life Associates of the Guild
				\item Members of the University Senate
				\item Members of the University Staff
				\item Students enrolled at the University of Western Australia.
			\end{enumerate}

		\subsection{Provisional Membership}
			Provisional membership shall be granted to any student studying any unit offered by the School of Computer Science and Software Engineering. \\
			Provisional members shall be considered to be ordinary members for the purposes of voting and as a part of the quorum in general meetings upon approval of the returning officer or chair.

		\subsection{Associateship of the Club}
			The Club, in general meeting, may from time to time admit to associateship persons who are, or have been:
			\begin{enumerate}[label=\alph*]
				\item Members of the Guild
				\item Associates of the Guild
				\item Honorary Life Associates of the Guild
				\item Members of the University Senate
				\item Members of the University Staff
				\item Students enrolled at the University of Western Australia.
				\item Ordinary members of the Club.
			\end{enumerate}
		\subsection{Honorary Life Memberships}
			The Club may in General Meeting by two-thirds majority of those present and voting confer Honorary Life Membership upon any member who has performed outstanding service to the Club.
            The Club may in General Meeting, by three-quarters of those present and voting remove Honorary Life Memberships upon an Honorary Life Member.
		\subsection{Primacy of Ordinary Members}
		Members other than Ordinary Members shall not:
		\begin{enumerate}[label=\alph*]
			\item Nominate candidates for the offices and Committee of the Club
			\item Become or remain office bearers of the Club
			\item Vote in the elections for the Committee of the Club
		\end{enumerate}
		But shall otherwise have all rights and privileges of ordinary members.
		\subsection{Council of Shadows}
		Any member who at any point has been, but no longer is an Executive Office bearer is considered to be a part of the council of shadows. The council of shadows does not exist and has no power over the day to day running or general direction of the club.
	\section{Subscription}

		\begin{enumerate}[label=\alph*]
			\item The annual subscription for financial members shall be a minimum of \$7.00 AUD, payable by the 30th of June on each year.

			\item The second-semester only subscription for financial members shall be a minimum of \$3.50 AUD, payable only after the 1st of July and before the 31st of December on each year.

			\item Members of the Guild shall receive a \$2.00 AUD discount on financial membership for a full year, or \$1.00 AUD after the 1st of July and before the 31st of December.

			\item Financial Membership is valid until March 1st the following year.
		\end{enumerate}

	\chapter{Meetings}

	\section{Meetings of the Club}
	\begin{enumerate}[label=\alph*]
		\item The Club shall hold its Annual General Meeting during the last six weeks of the University of Western Australia academic year, conversant with Provisions Governing General Meetings clause
		\item There shall be at least two ordinary General Meetings of the Club in each academic year
		\item The Committee may, at any time, call a Special General Meeting of the Club. The Secretary shall forthwith call a Special General Meeting upon receiving a written requisition from at least fifteen (15) financial ordinary members of the Club, and such meetings shall take place no later than two weeks immediately following receipt of such requisition. If the Secretary fails to call the meeting within that time, any of the signatories of the requisition may do so. Any business set out in the requisition shall have priority over all other business.
	\end{enumerate}

	\section{Provisions Governing General Meetings}
	\begin{enumerate}[label=\alph*]
		\item The Secretary or President shall cause written notice of any General Meeting together with the agenda therefore to be posted on the Computer Science Students social channels and in Guild Publications at least (7) seven days before the date appointed to that meeting

		\item No General Meeting may be held while a Guild General Meeting is in progress, provided that this shall not apply where the written notice of the meeting was given before the written notice of the Guild General Meeting. Any such meeting being conducted in contravention thereof shall disband immediately on the order of a disciplinary officer of the Guild.

		\item The quorum of General Meeting shall consist of ten(10) financial and ten(10) ordinary members who may or may not be the same people.

		\item All General Meetings of the Club shall be conducted in accordance with the procedure prescribed in the Standing Rules and Orders of the Guild Council
	\end{enumerate}



	\section{Elections}
	\begin{enumerate}[label=\alph*]

		\item The club shall hold Elections of its committee within the first six weeks of each Academic Year at the University of Western Australia.

		\item The club shall hold Elections for the next year's executive committee in the last six weeks of the Academic Year at the University of Western Australia. Newly elected officials take their position on the 1\textsuperscript{st} of January at midnight.

		\item Nominations for all positions shall be open for a minimum of five (5) days.

		\item On the last day of the nomination period, the club shall also hold its Annual General Meeting, where the business shall consist of candidate speeches for all nominations, in the order of committee precedence, followed by any other agenda items.

		\item A returning officer shall be appointed by the current club committee before the opening of nominations.

	\end{enumerate}

	\section{Provisions Governing Elections}
		\begin{enumerate}[label=\alph*]
			\item The Secretary or President shall cause written notice of the Annual Elections at least (7) seven days before the opening of nominations to be posted on the Computer Science Students social channels and in Guild Publications at least (7) seven days before the opening of nominations.
			\item At least seven (7) days before the opening of the nomination period, the Secretary shall call for nominations for the offices and Committee of the Club, and shall include the same in the notice of the Annual General Meeting. Nominations shall close at that meeting. The President may approve nominations surplus to that list during the meeting, before the vote.
			\item No Elections may be held while Guild Elections are in progress, provided that this shall not apply where the written notice of the Elections was given before the written notice of the Guild Elections. Any such elections shall not be considered binding upon the club, and will not satisfy the constitutional requirements for annual elections.
			\item The quorum of Annual Elections shall consist of five percent of all ordinary members.
			\item If quorum is not reached at an election, the results may be accepted by a properly constituted General Meeting of the club, which must be called by the outgoing Secretary immediately.
			\item Nomination via proxy shall be submitted prior to the beginning of the vote, In the case where a proxy hasn't delegated a representative who is present, the chair shall choose one on the candidates behalf.
			\item Proxy votes must be submitted via a secret ballot prior to the commencement of the election for the vote to be considered valid, pending approval from the returning officer.
			\item The validity of all candidates shall be determined by the returning officer. This is to ensure that an outside party is not able to seize the club by force or overwhelming numbers where it may not be in the best interest of the club. This is not to specifically exclude potential candidates where the returning officer disagrees with the individual, only for where the club is under legitimate threat.
			\item All Elections of the Club shall be conducted in accordance with the regulations governing Guild Elections, except where overruled by this constitution.
		\end{enumerate}

	\section{Committee Meetings}
	\begin{enumerate}[label=\alph*]
		\item The Committee shall meet as such times and places as the President shall determine
		\item The Secretary shall cause all members of the Committee to receive at least 3 days notice before the occurrence of any committee meeting
		\item The agenda of the meeting shall be created as the first item of business at each committee meeting. \\
		Any business previously added to the agenda shall take precedence in the meeting.
		\item The Secretary shall forthwith call a Special Meeting of the Committee upon receiving a written requisition from at least two members thereof; and such Special Meeting shall be held not later than 7 days immediately following the receipt of such requisition. \\
		If the Secretary fails to call the meeting within that time, any one of the members signing the requisition may do so. Any business set out in the requisition shall have priority over all other business
		\subsection{Quorum and Procedure of the Committee}
		\begin{enumerate}[label=\alph*]
		\item The quorum of the Committee shall be 3, of whom at least 3 shall be Office Bearers.
		\item All meetings of the Committee shall be conducted in accordance with the procedure prescribed in the Standing Rules and Orders of the Guild Council.
		\end{enumerate}
	\end{enumerate}

	\chapter{Committee Positions}
	\section{Executive Office Bearers}
	The Executive Office Bearers (Also referred to as the Executive Committee) of the Club shall be elected by the Ordinary Members of the Club at the Annual General Meeting and shall consist of, in order of seniority:
		\begin{enumerate}[label=\alph*]	
			\item The President
			\item The Vice President
			\item The Secretary
			\item The Treasurer
			\item The Marketing Officer
		\end{enumerate}

	\section{The Committee}
	The Committee of the Club shall consist of:
	\begin{enumerate}[label=\alph*]
		\item The Executive Office Bearers
		\item and the ordinary Committee which consists of:
		\begin{enumerate}[label=\roman*]
			\item Ordinary Committee Members\\
			who shall be elected from the ordinary members of the club.\\
			Whose numbers/purpose may change depending on club demand
		\end{enumerate}
		\item And non voting positions
		\begin{enumerate}
			\item Faculty Society Representative\\
			This position is to be left vacant to be filled by the Computer Science Student representative from the faculty society (At the time of writing that is The University Engineers Club)
			\item Immediate Past President\\
			Only the person who held the Elected Office Bearer position of President immediately preceding the commencement of the current President's term can be appointed Immediate Past President.
		\end{enumerate}
	\end{enumerate}

	\section{Conditions and Notes}
		\subsection{Eligibility} Only financial and ordinary members of the Club who are members of the Guild shall be eligible for election as office bearers and ordinary committee positions, however non-financial ordinary members may still nominate.\\
		A candidate defeated for one office may stand for any office lower on the list.

		\subsection{Exclusions} No Executive Office Bearer can hold more than one position simultaneously.

		\subsection{Election Format} Election shall be conducted by optional preferential ballot for each office in the order shown above.

		\subsection{Powers and Responsibilities} The powers and duties of each position are defined in subsequent Articles

	\section{Duration of Office}
		The office bearers and the committee members shall remain in office until their successors are to take over their respective position except when:
			\begin{enumerate}[label=\alph*]
			\item A vote is called and passed by a two thirds majority in any General Meeting to remove from office a member of the Committee whom is not doing their duties by the Club.\\
			Such a vote shall be declared as part of the business of the General Meeting no less than one week before the occurrence of any General Meeting or else it shall be considered invalid.
			\item Any office bearer who so wishes may resign their post as an office bearer or Committee Member with the provision that they give the Club 10 days notice prior to their resignation.
		\end{enumerate}
	\section{Vacancies}
		\begin{enumerate}[label=\alph*]
			\item If an office bearer resigns or ceases to hold office for any reason, the remaining members of the Committee shall forthwith fill the vacancy so created by appointing thereto a member of the	Committee, but such appointment shall be subject to review at the next General Meeting. Any Committee Member designated to fill this vacancy will not lose their original Committee position unless voted in.
			\item If an ordinary Committee member resigns or ceases to hold office for any reason, or is appointed an office bearer under Clause (a) above, then vacancy shall be filled by Committee from the ordinary membership, subject to review at the next General Meeting.
			\item Any Ordinary Committee Member, who is designated to fill the vacancy of an office bearer, if another ordinary member at a General Meeting fills the position, shall retain his/her position as Ordinary Committee Member.
			\item If another ordinary member who is not on Committee fills the office bearer vacancy, a vote to fill the ordinary Committee Position shall not be held unless the previous position holder has resigned.
		\end{enumerate}
	\section{Powers of Committee}
	Subject to this Constitution the Committee shall be responsible to the Club in General Meeting for giving effect to the objects of the Club as set out elsewhere in this constitution and for carrying out its everyday business, and without prejudice to the generality of the foregoing, the Committee shall have the power to:
	\begin{enumerate}[label=\alph*]
		\item acquire and dispose of property; to dispose of monies; to open banking accounts; and to enter into contracts. Unless acting under a special enabling resolution of a General Meeting, the Committee shall not borrow money or incur debts or liabilities on behalf of or in the name of the Club to a greater amount than five dollars for each and every then existing financial ordinary member of the Club.
		\item raise money for the Club by running events, providing that the monies used to fund this event does not exceed the provisions set out in Section a above
		\item make regulations and policies for the orderly and proper management of the affairs of the Club, but so that no regulation or policy is inconsistent or repugnant to this Constitution.
		\item make, alter, or repeat By-Laws, and to impose fines for the breach therefore. All By-Laws and any alteration or amendment thereof shall be subject to ratification by the Societies Council and the Guild Council before coming into force. The maximum fine imposed may not exceed five dollars (\$5.00)
	\end{enumerate}

	\section{Chair}
	The President shall have the right to take the chair at any meeting of the Club or of the Committee. \\
	If the President is absent or does not wish to exercise his right at any meeting, that right shall develop upon the Vice-President. \\
	In the event that both the President and Vice-President being absent or not wishing to exercise their right to the chair, that meeting shall elect its own chair.

	\section{Position Descriptions}
	In addition to any provisions set out elsewhere in this constitution or in any by laws or Regulations made hereunder, committee positions shall have the duty of:
		\subsection{President}
			\begin{enumerate}[label=\alph*]
				\item Generally carry out the policy of the club
				\item Coordinate and supervise the work of the Executive Officer Bearers, subject to the authority of the club in general meetings
				\item See that all Office-Bearers are conversant with the constitution and their respective duties and responsibilities
				\item Be commander-in-chief of the Air, Land, Naval, Cyber, Space and Time forces of the club.
			\end{enumerate}
		\subsection{Vice President}
			\begin{enumerate}[label=\alph*]
				\item Assist the president where-ever possible
				\item Carry out the responsibilities of President in the event of the incapacitation, untimely death or lengthy absence of the President; until such a time as a General Meeting can be called or the President can resume their duties.
			\end{enumerate}
		\subsection{Secretary}
			\begin{enumerate}[label=\alph*]
				\item To record all proceedings of the Club and the Committee in a Club Minute Book which they shall cause to be provided for that purpose:
				\item To conduct and keep copies of all correspondence of the Club:
					\begin{enumerate}[label=\roman*]
					\item To supply the Secretary of the Guild before the end of the first academic semester the information required to be recorded in the Guild register of the University societies.
					\item To notify the Secretary of the Guild within fourteen days of the alterations in the foregoing information.
					\item To lodge with the Secretary of the Guild a copy of the Constitution and any By-Laws made under its authority.
					\item To notify the Secretary of the Guild within fourteen days from the making therefore of any alterations to this Constitution of such By-Laws.
					\end{enumerate}
				\item To notify the Secretary of Societies Council and Public Affairs Council of the names of the delegate and deputy delegate to Societies Council and Public Affairs Council at least four days before meetings of these respective councils in each calendar year.
				\item In the event of the Club being de-registered, to present to the Guild Secretary within thirty days a duly audited statement of the financial position of the Club together with a copy of the resolution, which may have been passed by the Club as to the disposition of its funds.
			\end{enumerate}
		\subsection{Treasurer}
			\begin{enumerate}[label=\alph*]
				\item Keep proper books of account dealing with the property and finances of the Club and to furnish the Committee with such accounts and information relating to the finances and property of the Club as the Committee from time to time require.
				\item Arrange and be responsible for handling of the petty cash and to render an account to each Committee member of all petty cash.
				\item Prepare a financial statement showing all receipts and payments during their term of office, for presentation with auditors report to the Annual General Meeting.
				\item Produce and deliver all necessary books, vouchers and other documents to the persons appointed by the Guild Finance Committee for the purpose of conducting an audit, in so far as such persons may so required.
				\item Prepare necessary forms, and receipts for Societies Council in accordance with Semester \& O-day Grant Policies.
			\end{enumerate}
		\subsection{Marketing Officer}
            \begin{enumerate}[label=\alph*]
                \item Organise and manage the club's social media platforms.
                \item Produce and edit marketing material for the club, to be presented to the wider university and/or public audience.
                \item Act within the foremost capacity to promote and advertise the club to all who could be involved with the club.
            \end{enumerate}
		\subsection{Ordinary Committee Members}
			Assist the committee in the running of the club, including:
			\begin{enumerate}[label=\alph*]
				\item Attend committee meetings when available
				\item Assist Custodes with clubroom responsibilities
				\item Assist with the running of club events
			\end{enumerate}

		\subsection{Subcommittees}
			\begin{enumerate}[label=\arabic*]
			\item Ad-hoc Subcommittees
				The committee from time to time may make ad-hoc specialized subcommittees which may or may not be granted special powers to carry out their purpose until such a time that either their goal is done or the committee by majority vote choose to disband them.
			\item Ongoing Subcommittees 
				In addition there also exists ongoing subcommittees that have their powers, responsibilities and privileges outlined in Policies or Regulations.
				The Policies or Regulations which govern these subcommittees must be made publicly available wherever the elected committee finds best.
				Creation of, and changes to these Policies or Regulations for ongoing subcommittees must be passed at a general meeting and are subject to all the same validity requirements as changes to this constitution.
				The subcommittees have their rights granted to them from the elected committee and are subject to their decisions. These decisions may include but are not limited to decisions on membership to the subcommittee, changes in the rights and responsibilities to the subcommittee (within reason, and only until it can be ratified at the next general meeting) and the continuation of the subcommittees duties.
				Here is an officially recognised list of ongoing subcommittees
				\begin{enumerate}[label=\arabic*]
					\item Custodes (Translates to Guardians - Basically our "Door" group)
				\end{enumerate}
				\end{enumerate}

	\chapter{Miscellaneous}
		\section{History of Versions}
		    \begin{enumerate}[label=\arabic*]
			\item 2017 - The constitution was rewritten from scratch by President Anton Savill from a proposed 2012 version and the version that was put together by the 2015 committee when it was found that guild didn't have a copy of our actual constitution.
			\item 2018 - Modifications to the constitution from 1.0.2.0 to 1.0.5.0 Proposed by President Ki Savill
			\item 2022 - Modifications to the constitution from 1.0.6.0 to 1.0.9.3 Proposed by Vice-President Jordan Campbell
			\item 2025 - Modifications to the constitution from 1.0.9.4 to 1.1.0.0 Proposed by Vice-President Rory Cusworth
			\end{enumerate}
	    \section{Deposits and Withdrawal of Monies}
			\begin{enumerate}[label=\arabic*]
				\item All monies due and payable to the Club shall be received by the Treasurer who shall lodge them without undue delay for the credit of the Club.
				\item Any two members of the Executive may jointly sign cheques and forms of authority for the payment of funds of the Society.
				\item Not withstanding anything contained herein, no persons shall deposit or withdraw any monies into any account that Guild Council has closed by resolution.
			\end{enumerate}
		
		\section{Payments}
			No payments shall be made on behalf of the club or in the name of the club unless it has been authorised by the Executive Office Bearers.
		
		\section{Commercial Exploitation of the Club}
			The property and income of the Club shall be applied solely towards the promotion of the objects of the Club and no part of that property or income may be paid or otherwise distributed, directly or indirectly, to any person or body, except in good faith as compensation for services rendered or expenses incurred on behalf of the organisation.

		\section{Dissolution of the Club}
			% Modified from https://www.ato.gov.au/businesses-and-organisations/not-for-profit-organisations/getting-started/what-type-of-nfp-is-your-organisation
			In the event of the organisation being dissolved, the amount that remains after such dissolution and the satisfaction of all debts and liabilities shall be transferred to the Guild.
		
		\section{Patron}
		    \begin{enumerate}[label=\arabic*]
			  \item At any general meeting the club may elect a patron of the club, who may remain the patron of the club until the next general meeting of the club. \\
			\end{enumerate}
		\section{Caretaker Positions}
		     \begin{enumerate}[label=\arabic*]
		       \item In such a case no suitable candidate can be found for any position, the quorum of a general meeting may elect any willing party to become a caretaker, their obligations shall be identical to the position that they are filling, but at any point they may be challenged for the position by a more suitable candidate. There must also be a concerted effort to fill this position either before or at the next general meeting of the club.
             \end{enumerate}
		\section{Major Obligations to the Guild}
			\begin{enumerate}[label=\arabic*]
				\item The Club shall comply with the Regulation of the Guild, the Rules of Societies Council, and all other provisions enrolled upon the Guild Statutes book.
				\item All Office Bearers and committee members shall be jointly and severally responsible for such compliance, and shall be deemed liable in the event of noncompliance therewith.
			\end{enumerate}

		\section{Expulsion of Members}
			\begin{enumerate}[label=\arabic*]
				\item The Committee may by 3/4 vote request any member to resign from the Club, and in the event shall cause written notification of such request to be served upon the member concerned. The vote shall occur at a committee meeting.
				\item Should such a request prove ineffectual after fourteen days of written notification, the Committee may serve written notice of intended expulsion of the member concerned and should they not have resigned seven days after, the Committee may by unanimous vote expel him or her from the Club; but such expulsion shall be subject to review at the next General Meeting with the member present and to be heard.
			\end{enumerate}

		\section{Availability of Constitution}
			The Committee shall make available on request to all ordinary members this constitution. \\
			Hard Copies are to be offered at the cost of printing.

	\chapter{Interpretations and Amendments}

	\section{Interpretations}
		Subject to any provisions enrolled upon the Guild Statutes book and to any resolution passed by Guild Council, Societies Council or Public Affairs Council, the President shall have the power to interpret the meaning of any of the provisions contained in the Constitution, but the determining decision in case of doubt shall rest with the Club in General Meeting.
		\begin{enumerate}[label=\arabic*]
			\item 2.1.a, 2.3.a, 2.3.b make mention of the Universities Academic year. To avoid confusion this is referring to the standard teaching period excluding both "Summer Sessions" and "Winter Sessions" - Anton Savill 2017/10/22
			\item 3.8.3.a "a Club Minute Book" may also be a collection of digital documents written in plain English text. - Anton Savill  2017/11/24
		\end{enumerate}

	\section{Amendments}
		\begin{enumerate}[label=\alph*]
			\item Any two financial Ordinary Members of the Club may not less than three days before the day appointed for the next General Meeting submit to the Secretary a notice of motion signed by them proposing an alteration to this Constitution. This shall be posted on notice boards forthwith.
			\item A public pull request shall be made on which ever version control software the club elects to use (at the time of writing that is git hosted on GitHub) with details about the amendment.
			\item The motion may then be considered by the Club at its next meeting and amendments that are relevant to the subject matter thereof may be moved without notice.
			\item The motion of any amendment thereto shall not be deemed adopted unless it receives a two-thirds majority of the members present and voting.
			\item The motion as adopted with any amendments shall come into force as per guild rules and regulations.
		\end{enumerate}


\end{document}
