\documentclass[10pt,a4paper]{report}
\usepackage[margin=2cm]{geometry} %to modify page layout
\usepackage{titlesec} %to hide chapter titles
\usepackage{enumitem} %to have control over how formatting on enumerated lists

\setlength{\parindent}{0pt}

%because it's current year and clickable table of contents is needed
\usepackage{hyperref}
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}

\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}


\title{Computer Science Students Club Policy}
\author{Custodes}
\date{Effective 2018-10-23}


%To hide these full page chapter title page things which are just a waste of paper
\titleformat{\chapter}[display] {\normalfont\bfseries}{}{0pt}{\Large}


\begin{document}
	\maketitle
	\newpage
	\begin{small}
		\tableofcontents
	\end{small}
	\newpage
	\chapter{Description}
		\large{\textit{Quis custodiet ipsos custodes?}}
		\section{Purpose}
			The purpose of this subcommittee is to act as a approachable face for the club and to manage and maintain the clubroom.
			
			The members of this subcommittee may also be referred to as: Guardians, Watchmen or Watch people, Gatekeepers, Door members, or any other suitable title.
			
			Custos is the singular form of Custodes.
		\section{Qualifications of Members}
			Members of Custodes must:
			\begin{enumerate}
				\item Be considered trustworthy by the current committee.
				\item Be current student members of the University of Western Australia.
				\item Be willing to accept and carry out all legal directives given to them by committee.
			\end{enumerate}
			Additionally all executive members of the committee are automatically Custodes.
	\chapter{Responsibilities}
		\section{Main Responsibilities}
		\begin{enumerate}
			\item Custodes are to do everything which may be reasonably expected of them in order to protect the members and property of the club.
			\item Custodes are responsible for the oversight of all activities in the clubroom while it is under their control.
			\item Custodes are to assist any person looking to become a member of the club.
			\item Custodes are expected to attend clubroom cleaning sessions as announced by the committee or give appropriate apologies.
		\end{enumerate}
		\section{Supplementary Responsibilities}
			\subsection{Room}
			\begin{enumerate}
				\item There may only be people in the clubroom if there is a Custos in the room. This Custos is said to be "holding the room".
				\item If any Custos is present in the room, the clubroom must be open.
				\item A Custos may not hold the room open if they are engaged in any activity that significantly reduces their ability to act in accordance with their station.
				\item If a Custos solely holds the room and intends to leave, they should give as much notice as possible to all members in the room that this is the case and therefore the room will be closing.
				\item If no other Custos arrives during this time, all members must leave and the departing Custos must close the room before leaving.
				\item If a new Custos arrives and is able to hold the room open, then it can be assumed this responsibility is passed to this member.
				\item It is expected that the leaving Custos shall inform the newly arrived Custos that they are now holding the room as a matter of course.
				\item A Custos may bestow upon a trusted member temporary Custos rights, these rights may not be transferred or bestowed again from the recipient and last for a maximum of 3 hours. - The original Custos is still considered responsible for the state of the room and so should select who they bestow it upon carefully.
			\end{enumerate}
			
	\chapter{Rights, Powers and Privileges}
		\section{Powers given by Committee to fulfill Subcommittee Purpose}
		
		\begin{enumerate}
			\item To assist with their responsibilities under, Custodes are given powers to assist in the safe and secure management of the clubroom.
			\item A Custos may use their powers whenever and however they see fit, though any use or abuse of Custodes Powers may be subject to review by the committee, and may result in the loss of Custodes status.
			\item Custodes have the power to expel any member from the clubroom as detailed in the appendices.
		\end{enumerate}
		
		\section{Additional Powers granted in specific circumstances}
		\begin{enumerate}
			\item In the circumstance where there is someone looking to speak to someone from the club, a Custos may take action to address this person as seen appropriate. Any action taken by the Custos must be noted down and sent to the committee
		\end{enumerate}
		
		\section{Items that Custodes should be aware of}
		\subsection{UWA Security Contact Details}
		\begin{itemize}
			\item Emergency: 6488 2222
			\item Non-Emergency: 6488 3020
		\end{itemize}
		\subsection{Keeping the Room Open}
		Custodes should endeavour to maintain the clubroom and its contents in an appropriate and usable state.\\
		Custodes should ensure people do not litter in the clubroom.\\
		Rubbish bins are provided by the club to assist in keeping the clubroom tidy.\\
		Large items such as cardboard boxes (including pizza boxes) should not to be put in the bins, and should instead be taken down to the bins directly on leaving the clubroom.\\
		If the bins get too full, it is the responsibility of Custodes present to ensure they are emptied
		
		\subsection{Reasons for Expulsion}
		In most cases, offenders should be given a warning before being expelled
		The following is a non-exhaustive list of appropriate reasons for expulsion:
		\begin{itemize}
			\item Violent, offensive, or disruptive behaviour
			\item Danger or damage to members or club or member property
			\item Habitual littering
		\end{itemize}
		In the event that an offender refuses to abide by the expulsion, UWA Security can be called
		
		
	\chapter{Appendices}
		\section{Length of Term}
		\subsection{General}
		The list of Custodes shall, at the committee's discretion, be purged and recreated during the End of Year Annual General Meeting so as to maintain an accurate list of members who are 'trusted' and who currently require access to the clubroom.
		\subsection{Circumstantial}
		\begin{enumerate}
			\item A Custos can, at any time, be removed from the list of Custodes with or without prior notice or reason by the committee.
			\item A member may appeal such a decision at any Ordinary Committee Meeting.
		\end{enumerate}
		
		\section{Expulsion}
		From time to time it may be seen necessary to expel someone from the clubroom for a limited amount of time.
		\begin{enumerate}
			\item A person who is expelled is forbidden entry to the clubroom for the duration of the expulsion.
			\item An expelled person may enter the clubroom with an acceptable reason under the oversight and with the permission of the active Custos.
			\item An expulsion expires either once the conditions set by the Custos have been met, or at the next Ordinary Committee Meeting, whichever comes sooner.
			\item The committee is able to revoke this expulsion if they deem the action taken by the Custos to be unjust.
			\item All expulsions are subject to review at the next Ordinary Committee Meeting, at which the committee will decide what further action to take, if any.
			\item A Custos is obligated to notify the other Custodes and the committee in a form of electronic communication whenever a person is expelled with details of the situation, exactly what actions were taken and conditions of the expulsion.
			\item This power is expressly intended to enable Custodes in their above responsibilities, though may also be used to prevent or punish disruption and misbehaviour.
		\end{enumerate}
		
		\section{Leader of the Custodes}
		The Custodes may, at the presidents discretion, elect a "leader". This "leader" has no special powers or status among the Custodes or committee, except for being a figurehead. This figurehead may elect to take the title of "Sam Vimes" if they wish.\\
		If anyone ever questions the position of the Custodes, i.e. "Quis custodiet ipsos custodes?" or "Who watches the watchmen" etc. Custodes must either answer with "Sam Vimes" or the leaders name. If the leader is asked this question they must answer "I Do" and then must show the member this section of the policy and explain that it's a Discworld reference.
		
	\chapter{Acknowledgments}
		The initial version of this document has liberal amount adapted from the UCC Door Policy (Version 1.0, 2015-03-17)  - the current version can be found here: https://www.ucc.asn.au/infobase/policies/door.ucc
\end{document}