\documentclass[10pt,a4paper]{report}
\usepackage[margin=2cm]{geometry} % to modify page layout
\usepackage{titlesec} % to hide chapter titles
\usepackage{enumitem} % to have control over how formatting on enumerated lists

% because it's 2017 and clickable table of contents is needed
% it's 2026 and I still agree - Ethan
\usepackage{hyperref}
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}

\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}


\title{Computer Science Students Club Policy}
\author{Marketing Subcommittee}
\date{02-02-2026}


% To hide these full page chapter title page things which are just a waste of paper
\titleformat{\chapter}[display] {\normalfont\bfseries}{}{0pt}{\Large}


\begin{document}
	\maketitle
	\newpage
	\begin{small}
		\tableofcontents
	\end{small}
	\newpage

	\chapter{Description}
		\section{Purpose}
		The purpose of the Marketing Subcommittee is to actively promote the club's events, initiatives, and presence both within the university and externally. Members serve as the creative and communicative voice of the CSSC, ensuring strong engagement with club members, potential club members, and the broader community.

		\section{Qualifications of Members}
		Members of the Marketing Subcommittee must:
		\begin{enumerate}[label=\arabic*.]
			\item Be current full privileged members of the Computer Science Students' Club.
			\item Be willing to actively represent the club positively and publicly.
			\item Be elected at an Ordinary General Meeting (OGM) or appointed at the discretion of the committee.
			\item Agree to follow directions from the committee and act within the club's constitution and policy guidelines.
		\end{enumerate}

		The number of Marketing Subcommittee members is flexible and determined by the committee. The size and members of the Marketing Subcommittee are to be revaluated at the beginning of each semester.  

	\chapter{Responsibilities}
		\section{Main Responsibilities}
		\begin{enumerate}[label=\arabic*.]
			\item Promote all CSSC events through social media, print, and campus visibility.
			\item Maintain and update club social media platforms, event pages, and digital communications.
			\item Assist in designing posters, videos, or other promotional materials.
			\item Contribute to increasing club membership and engagement through outreach campaigns.
		\end{enumerate}

		\section{Supplementary Responsibilities}
		\begin{itemize}
			\item Attend and capture content at club events (e.g., photos, short interviews).
			\item Assist in writing and distributing newsletters or promotional emails.
			\item Monitor online engagement and suggest improvements to club outreach strategy.
		\end{itemize}

	\chapter{Rights, Powers and Privileges}
		\section{Powers given by Committee to fulfill Subcommittee Purpose}
		\begin{enumerate}[label=\arabic*.]
			\item Permission to manage the club's official digital channels (e.g., Facebook, Instagram, Discord).
			\item Authority to initiate club promotions under the guidance of the committee.
			\item Creative license to design branding assets consistent with club identity.
		\end{enumerate}

		\section{Additional Powers granted in specific circumstances}
		\begin{enumerate}[label=\arabic*.]
			\item With committee approval, collaborate with external organisations, sponsors, or other UWA clubs for cross-promotion.
			\item Recommend and trial new outreach tools or platforms, subject to committee review.
		\end{enumerate}

	\chapter{Other Important Notes}
		\section{Length of Term}
		Marketing Subcommittee members will serve until the start of a new semester unless removed by the committee.

		\section{Removal and Replacement}
		Members may be removed by a committee vote due to inactivity, misconduct, or misrepresentation. Replacement members may be appointed or elected at the committee's discretion.

		\section{Acknowledgments}
		This document is based on the structure and style of the CSSC \textit{Custodes} policy and was adapted in 2026.

\end{document}
